\begin{poem}{At the round earth's imagin'd corners}{15mm}
  \tagline{by John Donne}
  \begin{stanza}
    At the round earth's imagin'd corners, blow
Your trumpets, angels, and arise, arise
From death, you numberless infinities
Of souls, and to your scatter'd bodies go;
All whom the flood did, and fire shall o'erthrow,
All whom war, dearth, age, agues, tyrannies,
Despair, law, chance hath slain, and you whose eyes
Shall behold God and never taste death's woe.
But let them sleep, Lord, and me mourn a space,
For if above all these my sins abound,
'Tis late to ask abundance of thy grace
When we are there; here on this lowly ground
Teach me how to repent; for that's as good
As if thou'hadst seal'd my pardon with thy blood.
\end{stanza}
\end{poem}

\begin{poem}{There was an old man}{15mm}
  \tagline{By Edward Lear}
  \begin{stanza}
    There was an old man with a beard
    Who said, `It is just as I feared
    \qquad Two owls and a wren
    \qquad three larks and a hen
    Have all made their nests in my beard!
  \end{stanza}
\end{poem}

\begin{poem}{Say not!}{15mm}
  \tagline{By A. H, Clough}
  \begin{stanza}
    Say not, the struggle naught availeth
    \qquad the labour and the wounds are vain
    the enemy faints not, nor faileth
    \qquad and as things have been, things remain.
  \end{stanza}
  \begin{stanza}
    Say not, the struggle naught availeth!
    \qquad it may be in yon smoke concealed
    your comrades chase e'en now the fliers
    \qquad and but for you possess the field
  \end{stanza}
  \begin{stanza}
    Seen here the tired waves, vainly breaking
    \qquad seem no painful inch to gain
    but far back through creeks and inlets making
    \qquad comes silent, flooding in, the main.
  \end{stanza}
  \begin{stanza}
    Not through Eastern windows only
    \qquad with the dawn comes in the light
    Ahead the sun climbs, O, so slowly
    \qquad but Westward look! the land is bright!
  \end{stanza}
\end{poem}

\begin{poem}{Pied Beauty}{15mm}
  \tagline{By G M Hopkins}
  \begin{stanza}
  Glory be to God for dappled things –
  \quad   For skies of couple-colour as a brinded cow;
  \qquad    For rose-moles all in stipple upon trout that swim;
Fresh-firecoal chestnut-falls; finches’ wings;
  \quad Landscape plotted and pieced – fold, fallow, and plough;
  \qquad    And áll trádes, their gear and tackle and trim.
\end{stanza}
\begin{stanza}
All things counter, original, spare, strange;
\quad   Whatever is fickle, freckled (who knows how?)
\qquad      With swift, slow; sweet, sour; adazzle, dim;
He fathers-forth whose beauty is past change:
\hfill                                Praise him.\qquad
\end{stanza}
\end{poem}
%%% mode: latex
%%% TeX-master: "book"
%%% End:
